---
title: "tripo3d: Image-to-3D in R"
author: "tripo3d authors"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tripo3d: Image-to-3D in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Setup

Set your Tripo API key once per session:

```{r}
library(tripo3d)
tripo_setup(api_key = "your-tripo-api-key")
```

Alternatively, set the `TRIPO_API_KEY` environment variable before starting R.

## One-shot generation

The simplest workflow: pass an image, get back a viewable 3D model.

```{r}
model <- generate_3d("path/to/photo.jpg")

model
# <tripo_model>
#   Path: /home/user/.cache/R/tripo3d/task_abc123.glb
#   Task:  task_abc123
#   Format: glb
```

## Step-by-step workflow

If you need more control over the process:

```{r}
task <- create_3d_from_image("path/to/photo.jpg")
task
# <tripo_task>
#   Status: running
#   Task:   task_abc123

result <- poll_task(task, interval = 3, max_wait = 120)
result
# <tripo_task>
#   Status: success
#   Model:  https://api.tripo3d.ai/v2/models/model_xyz.glb

model <- download_model(result)
model
```

## Viewing 3D models

```{r}
view_3d(model)
```

You can also view a `.glb` file directly:

```{r}
view_3d("path/to/downloaded/model.glb")
```

The viewer supports orbit (left drag), pan (right drag), and zoom (scroll).

## Configuration

```{r}
# Custom timeout and cache directory
tripo_setup(
  api_key = "your-key",
  timeout = 120,
  output_dir = "~/my_3d_models"
)
```

## Shiny integration

```{r, eval = FALSE}
library(shiny)

ui <- fluidPage(
  glb_viewer_output("viewer", height = "600px")
)

server <- function(input, output, session) {
  model <- generate_3d("photo.jpg")
  output$viewer <- render_glb_viewer({
    view_3d(model)
  })
}

shinyApp(ui, server)
```
